\large{Vipassana for Hackers} \\ \Huge{Paper Two: The Brain} \\ \large\textit{Version 0.2}

### 2019-10-07 paper-two/paper-two.tex
more edits to grammar in IPL section

The Inferior Parietal lobe (IPL) is situated in the back of the brain and it is
involved in the perception of facial stimuli. \cite{ipl}.In a study previously conducted where
subjects were asked to retrieve previous judgments about oneself, their friend and the Dutch queen, 
the activation of the IPL decreased with decreasing self reference. \cite{iplself} 
Another study used Transcranial Magnetic Stimulation (TMS) to create a sort of virtual lesion of
the right-IPL and showed that this disrupts self-other discrimination. \cite{ipltms}

>>>>

The Inferior Parietal lobe (IPL) is situated in the back of the brain and it is
involved in the perception of facial stimuli. \cite{ipl}
The IPL has been hypothesized as being involved in distinguishing self from others, 
in a study where subjects were asked to retrieve 
previous judgments about oneself, their friend and the Dutch queen, 
the activation of the IPL was seen to decrease with decreasing self-reference. \cite{iplself} 
Another study also used Transcranial Magnetic Stimulation (TMS) to create a sort of "virtual lesion" 
(transiently disturb the neural circuitry in that area) of
the right-IPL and showed that this disrupts self-other discrimination. \cite{ipltms}
